Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2018-04-20 inst/examples/20170201-manuscript.Rmd
ok

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")
knitr::opts_chunk$set(fig.width=13.5,fig.height=8)

@@

  p <- p + guides(
       color = guide_legend(keywidth = 5, title = "Gatherings"),
        fill = guide_legend(keywidth = 5, title = "Gatherings"),     
       shape = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE),
    linetype = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE))

>>>>

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
#knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
# knitr::opts_chunk$set(dev = "Cairo")
#knitr::opts_chunk$set(dev = "CairoPDF")
knitr::opts_chunk$set(dev = "CairoPS")
# knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")
knitr::opts_chunk$set(fig.width=13.5,fig.height=8)

@@

  p <- p + guides(
       color = guide_legend(keywidth = 5, title = "Quires"),
        fill = guide_legend(keywidth = 5, title = "Quires"),     
       shape = guide_legend(keywidth = 5, title = "Quires", reverse = TRUE),
    linetype = guide_legend(keywidth = 5, title = "Quires", reverse = TRUE))
